---
title: Analyses in A Randomized Study to Evaluate the Effect of a Nudge via Weekly
  Emails on Students' Attitudes Towards Statistics
author: "Nathan Taback"
date: "July 25, 2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE,message=FALSE)
library(gmodels)
library(tidyverse)
library(reshape2)
library(cowplot)
library(readr)
library(lsmeans)
library(broom)
library(knitr)
library(kableExtra)
library(janitor)
```

# Introduction

This document shows the analyses described in the article: A Randomized Study to Evaluate the Effect of a Nudge via Weekly Emails on Students' Attitudes Towards Statistics by Nathan Taback and Alison Gibbs.

# Read in data

```{r}

dat2016_cons <- read_csv("effectofnudge.csv")

# create Boolean variable for missing

no_miss <- (
  is.na(dat2016_cons$change_affect) == F &
    is.na(dat2016_cons$change_cog) == F &
    is.na(dat2016_cons$change_difficulty) == F &
    is.na(dat2016_cons$change_effort) == F &
    is.na(dat2016_cons$change_interest) == F &
    is.na(dat2016_cons$change_value) == F
)

# create dataframe with all students that completed SATS-36

dat2016_complete <- dat2016_cons %>% filter(no_miss)
```


# Table 3 - Distribution of student characteristics by intervention

```{r}
# use janitor lib to create table with pcts.

t1 <- dat2016_complete %>% tabyl(cgpa, email) %>% 
  adorn_totals(c("col")) %>%
  adorn_percentages("col") %>% 
  adorn_pct_formatting(digits = 0) %>% 
  adorn_ns(position = "front") %>% rename("X1" = cgpa)

t2 <- dat2016_complete %>% tabyl(sex, email) %>% 
  adorn_totals(c("col")) %>%
  adorn_percentages("col") %>% 
  adorn_pct_formatting(digits = 0) %>% 
  adorn_ns(position = "front") %>% rename("X1" = sex)
  
t3 <- dat2016_complete %>% #replace_na(list(Year = "Missing")) %>% 
  tabyl(Year, email) %>% 
  adorn_totals(c("col")) %>%
  adorn_percentages("col") %>% 
  adorn_pct_formatting(digits = 0) %>% 
  adorn_ns(position = "front") %>% rename("X1" = Year)

t4 <- dat2016_complete %>% 
  tabyl(Section, email) %>% 
  adorn_totals(c("col")) %>%
  adorn_percentages("col") %>% 
  adorn_pct_formatting(digits = 0) %>% 
  adorn_ns(position = "front") %>% rename("X1" = Section)

t5 <- rbind(t1,t2,t3,t4) %>% rename(" " = X1)

t6 <- kable(t5, format = "html", booktabs = T, caption = "Participating students by type of email") %>%
  add_header_above(c(" " = 1, "Type of Email" = 2, " " = 1)) %>%
  kable_styling() %>%
  pack_rows(group_label = "CGPA", start_row = 1, end_row = 4, latex_gap_space = "1em") %>%
  pack_rows(group_label = "Sex", start_row = 5, end_row = 6, latex_gap_space = "1em") %>%
  pack_rows(group_label = "Year of Study", start_row = 7, end_row = 11, latex_gap_space = "1em") %>%
  pack_rows(group_label = "Course Section", start_row = 12, end_row = 18, latex_gap_space = "1em")

t6
```

# Table 4

```{r}

sat_complete_tab4 <- function(sats)
{
  dim_name <- expr({{sats}})
  dim_name <- quo_name(dim_name)
  
  dat2016_cons %>% 
  mutate(comp_aff = !is.na({{sats}})) %>%
  group_by(comp_aff, email) %>% summarise(n = n()) %>%
  spread(email, n) %>%
  rowwise() %>%
    filter(comp_aff == TRUE) %>%
    mutate(Total=sum(Interesting + Plain),
         p1 = round(Interesting/703*100),
         p2 = round(Plain/727*100),
         p3 = round(Total/1430*100)) %>%
    select(Interesting, p1, Plain, p2 ) %>% 
    ungroup() %>% 
    select(c(-1)) %>% 
    mutate(dimension = dim_name)
}

# table 4

r1 <- cbind(sat_complete_tab4(affect_pre), sat_complete_tab4(affect_post))

r2 <- cbind(sat_complete_tab4(cog_pre), sat_complete_tab4(cog_post))

r3 <- cbind(sat_complete_tab4(difficulty_pre), sat_complete_tab4(difficulty_post))

r4 <- cbind(sat_complete_tab4(effort_pre), sat_complete_tab4(effort_post))

r5 <- cbind(sat_complete_tab4(interest_pre), sat_complete_tab4(interest_post))

r6 <- cbind(sat_complete_tab4(value_pre), sat_complete_tab4(value_post))

rbind(r1, r2, r3, r4, r5, r6)

```



# Table 5


```{r}

sat_complete_tab5 <- function(sats)
{
  dim_name <- expr({{sats}})
  dim_name <- quo_name(dim_name)
  
  dat2016_cons %>% 
  mutate(comp_aff = !is.na({{sats}})) %>%
  group_by(comp_aff, email) %>% summarise(n = n()) %>%
  spread(email, n) %>%
  rowwise() %>%
  mutate(Total=sum(Interesting + Plain),
         p1 = round(Interesting/703*100),
         p2 = round(Plain/727*100),
         p3 = round(Total/1430*100)) %>%
    select(comp_aff, Interesting, p1, Plain, p2, Total,p3 ) %>%
    filter(comp_aff == TRUE) %>%
    ungroup() %>% 
    select(c(-1)) %>% 
    mutate(dimension = dim_name)
}


# change measures are not missing if completed both 
# pre and post



t1 <- sat_complete_tab5(change_affect) 
t2 <- sat_complete_tab5(change_cog)
t3 <- sat_complete_tab5(change_difficulty)
t4 <- sat_complete_tab5(change_effort)
t5 <- sat_complete_tab5(change_interest)
t6 <- sat_complete_tab5(change_value)


rbind(t1, t2, t3, t4, t5, t6)
```


# Missing data patterns

```{r}
library(mice)

# missing value patterns - pre
dat2016_cons |> 
  select(ends_with("pre")) |> 
  md.pattern(rotate.names = T, plot = F)

# count missing value patterns - pre
dat2016_cons |> 
  select(ends_with("pre")) |> 
  md.pattern(rotate.names = T, plot = F) |> NROW() - 1
  

# missing value patterns - post
dat2016_cons |> 
  select(ends_with("post")) |> 
  md.pattern(rotate.names = T, plot = F) 


# count missing value patterns - post
dat2016_cons |> 
  select(ends_with("post")) |> 
  md.pattern(rotate.names = T, plot = F) |> NROW() - 1


# missing value patterns - pre or post
dat2016_cons |> 
  select(ends_with("post") | ends_with("pre")) |> 
  md.pattern(rotate.names = T, plot = F) 

# count missing value patterns - pre or post
dat2016_cons |> 
  select(ends_with("post") | ends_with("pre")) |> 
  md.pattern(rotate.names = T, plot = F) |> NROW() - 1

```

# Figure 3

```{r}

datbp <- dat2016_cons %>%
  select(affect_pre,
         cog_pre,
         value_pre,
         difficulty_pre,
         interest_pre,
         effort_pre,
         email) %>%
  gather(attitude, change_value, -email) %>%
  mutate(email = recode(email, "Plain" = "No Nudge", "Interesting" = "Nudge"))


datbp$attitude <-
  recode(
    datbp$attitude,
    "affect_pre" = "Affect",
    "cog_pre" = "Cognative",
    "value_pre" = "Value",
    "difficulty_pre" = "Difficulty",
    "interest_pre" = "Interest",
    "effort_pre" = "Effort"
  )

ggplot(datbp, aes(x = attitude, y = change_value, fill = email)) +
  geom_boxplot() +
  scale_fill_manual(values = c("black", "grey"), name = "Weekly Email Digest") +
  labs(x = "Attitude", y = "Pre Course Attitude Score") +
  theme(
    axis.text = element_text(size = 10),
    axis.title = element_text(size = 14, face = "bold"),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black")
  )

```


# Table 6

```{r}
CrossTable(dat2016_complete$Open_Email, dat2016_complete$email ,missing.include = T,prop.chisq=F)
```

# Figure 4

```{r}
mod1 <-
  lm((affect_post - affect_pre) ~ affect_pre + cgpa + sex + Section + email +
       Open_Email,
     data = dat2016_cons)
summary(mod1)
mod1.ls <- lsmeans(mod1, "email")
mod1.ls
contrast(mod1.ls, "trt.vs.ctrl")
a1 <- confint(contrast(mod1.ls, "trt.vs.ctrl"), level = 1 - (0.05 / 6))
a1$att <- "Affect"


mod1 <-
  lm((cog_post - cog_pre) ~ cog_pre + cgpa + sex + Section + email + Open_Email,
     data = dat2016_cons)
summary(mod1)
mod1.ls <- lsmeans(mod1, "email")
mod1.ls
contrast(mod1.ls, "trt.vs.ctrl")
a2 <- confint(contrast(mod1.ls, "trt.vs.ctrl"), level = 1 - (0.05 / 6))
a2$att <- "Cognitive"

mod1 <-
  lm((value_post - value_pre) ~ value_pre + cgpa + sex + Section + email +
       Open_Email,
     data = dat2016_cons)
summary(mod1)
mod1.ls <- lsmeans(mod1, "email")
mod1.ls
contrast(mod1.ls, "trt.vs.ctrl")
a3 <- confint(contrast(mod1.ls, "trt.vs.ctrl"), level = 1 - (0.05 / 6))
a3$att <- "Value"

mod1 <-
  lm((difficulty_post - difficulty_pre) ~ difficulty_pre + cgpa + sex + Section +
       email + Open_Email,
     data = dat2016_cons
  )
summary(mod1)
mod1.ls <- lsmeans(mod1, "email")
mod1.ls
contrast(mod1.ls, "trt.vs.ctrl")
a4 <- confint(contrast(mod1.ls, "trt.vs.ctrl"), level = 1 - (0.05 / 6))
a4$att <- "Difficulty"

mod1 <-
  lm((interest_post - interest_pre) ~ interest_pre + cgpa + sex + Section +
       email + Open_Email,
     data = dat2016_cons
  )
summary(mod1)
mod1.ls <- lsmeans(mod1, "email")
mod1.ls
contrast(mod1.ls, "trt.vs.ctrl")
a5 <- confint(contrast(mod1.ls, "trt.vs.ctrl"), level = 1 - (0.05 / 6))
a5$att <- "Interest"

mod1 <-
  lm((effort_post - effort_pre) ~ effort_pre + cgpa + sex + Section + email +
       Open_Email,
     data = dat2016_cons)
summary(mod1)
mod1.ls <- lsmeans(mod1, "email")
mod1.ls
contrast(mod1.ls, "trt.vs.ctrl")
a6 <- confint(contrast(mod1.ls, "trt.vs.ctrl"), level = 1 - (0.05 / 6))
a6$att <- "Effort"


a <- rbind(a1, a2, a3, a4, a5, a6)

ggplot(a, aes(x = att, y = estimate)) +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL),
                colour = "black",
                width = .2) +
  geom_point(size = 4) +
  labs(title = "Difference Between Post Course Attitudes by Weekly Email Digest Type", x =
         "",
       y = "Adjusted 99% CI for Difference of SATS-36 Gain Score (No Nudge - Nudge)") +
  geom_hline(aes(yintercept = 0)) +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 90, size = 8, face = "bold"),
    axis.text.y = element_text(size = 8),
    axis.title.y = element_text(size = 8, face = "bold"),
    axis.ticks.x = element_blank(),
    axis.line.x = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank(),
    axis.line = element_line(colour = "black")
  )
```

# Figure 4 - among students that only opened email

```{r}
mod1 <- lm((affect_post-affect_pre)~affect_pre +cgpa+sex+Section+email+Open_Email,data = dat2016_cons[dat2016_cons$Open_Email==1,])
summary(mod1)
mod1.ls <- lsmeans(mod1,"email")
mod1.ls
contrast(mod1.ls,"trt.vs.ctrl")
a1 <- confint(contrast(mod1.ls,"trt.vs.ctrl"), level = 1-(0.05/6))
a1$att <- "Affect"


mod1 <- lm((cog_post-cog_pre)~cog_pre +cgpa+sex+Section+email+Open_Email,data = dat2016_cons[dat2016_cons$Open_Email==1,])
summary(mod1)
mod1.ls <- lsmeans(mod1,"email")
mod1.ls
contrast(mod1.ls,"trt.vs.ctrl")
a2 <- confint(contrast(mod1.ls,"trt.vs.ctrl"), level = 1-(0.05/6))
a2$att <- "Cognitive"

mod1 <- lm((value_post-value_pre)~value_pre +cgpa+sex+Section+email+Open_Email,data = dat2016_cons[dat2016_cons$Open_Email==1,])
summary(mod1)
mod1.ls <- lsmeans(mod1,"email")
mod1.ls
contrast(mod1.ls,"trt.vs.ctrl")
a3 <- confint(contrast(mod1.ls,"trt.vs.ctrl"), level = 1-(0.05/6))
a3$att <- "Value"

mod1 <- lm((difficulty_post-difficulty_pre)~difficulty_pre +cgpa+sex+Section+email+Open_Email,data = dat2016_cons[dat2016_cons$Open_Email==1,])
summary(mod1)
mod1.ls <- lsmeans(mod1,"email")
mod1.ls
contrast(mod1.ls,"trt.vs.ctrl")
a4 <- confint(contrast(mod1.ls,"trt.vs.ctrl"), level = 1-(0.05/6))
a4$att <- "Difficulty"

mod1 <- lm((interest_post-interest_pre)~interest_pre +cgpa+sex+Section+email+Open_Email,data = dat2016_cons[dat2016_cons$Open_Email==1,])
summary(mod1)
mod1.ls <- lsmeans(mod1,"email")
mod1.ls
contrast(mod1.ls,"trt.vs.ctrl")
a5 <- confint(contrast(mod1.ls,"trt.vs.ctrl"), level = 1-(0.05/6))
a5$att <- "Interest"

mod1 <- lm((effort_post-effort_pre)~effort_pre +cgpa+sex+Section+email+Open_Email,data = dat2016_cons[dat2016_cons$Open_Email==1,])
summary(mod1)
mod1.ls <- lsmeans(mod1,"email")
mod1.ls
contrast(mod1.ls,"trt.vs.ctrl")
a6 <- confint(contrast(mod1.ls,"trt.vs.ctrl"), level = 1-(0.05/6))
a6$att <- "Effort"


a <- rbind(a1,a2,a3,a4,a5,a6)

ggplot(a, aes(x=att, y=estimate)) + 
  geom_errorbar(aes(ymin=lower.CL, ymax=upper.CL), colour="black", width=.2) + 
  geom_point(size=4) +
  labs(title="Difference Between Post Course Attitudes by Weekly Email Digest Type",x="", 
       y="Adjusted 99% CI for Difference of Post SATS-36 Score (Plain - Interesting)") +
  geom_hline(aes(yintercept=0)) +
  theme(legend.position="none", axis.text.x = element_text(angle=90,size = 8, face = "bold"), 
        axis.text.y = element_text(size = 8),
        axis.title.y = element_text(size = 8, face = "bold"),
        axis.ticks.x = element_blank(),axis.line.x = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "black"))

```


# Table 7

```{r}
mod2 <-
  lm(coursemark ~ email + cgpa + Section, data = dat2016_complete)
summary(mod2)
mod2.ls <- lsmeans(mod2, "email")
mod2.ls
contrast(mod2.ls, "trt.vs.ctrl")
confint(contrast(mod2.ls, "trt.vs.ctrl"), level = .95)

mod2 <-
  lm(coursemark ~ email + cgpa + Section,
     data = dat2016_complete[dat2016_complete$Open_Email == 0,])
summary(mod2)
mod2.ls <- lsmeans(mod2, "email")
mod2.ls
contrast(mod2.ls, "trt.vs.ctrl")
confint(contrast(mod2.ls, "trt.vs.ctrl"), level = .95)


mod2 <-
  lm(coursemark ~ email + cgpa + Section,
     data = dat2016_complete[dat2016_complete$Open_Email == 1,])
summary(mod2)
mod2.ls <- lsmeans(mod2, "email")
contrast(mod2.ls, "trt.vs.ctrl")
confint(contrast(mod2.ls, "trt.vs.ctrl"), level = .95)
```

# Table 8

```{r}
make_table_mean <- function(c1){
  dat2016_complete %>% 
    select(ID,email, {{c1}}) %>% 
    pivot_longer(cols = {{c1}}, 
               names_to = "categ", values_to = "value") %>%
    group_by(email, categ) %>%
    summarise(m = round(mean(value),2)) %>%
    pivot_wider(names_from = email, values_from = c(m))
}

make_table_sd <- function(c1){
  dat2016_complete %>% 
    select(ID,email, {{c1}}) %>% 
    pivot_longer(cols = {{c1}}, 
               names_to = "categ", values_to = "value") %>%
    group_by(email, categ) %>%
    summarise(m = round(sd(value),2)) %>%
    pivot_wider(names_from = email, values_from = c(m))
}


#pre-mean
t1 <- make_table_mean("affect_pre")
t2 <- make_table_mean("cog_pre")
t3 <- make_table_mean("value_pre")
t4 <- make_table_mean("difficulty_pre")
t5 <- make_table_mean("interest_pre")
t6 <- make_table_mean("effort_pre")

pre_mean <- rbind(t1,t2,t3,t4,t5,t6)
  
#pre-sd
t1 <- make_table_sd("affect_pre") 
t2 <- make_table_sd("cog_pre")
t3 <- make_table_sd("value_pre")
t4 <- make_table_sd("difficulty_pre")
t5 <- make_table_sd("interest_pre")
t6 <- make_table_sd("effort_pre")

pre_sd <- rbind(t1,t2,t3,t4,t5,t6)


#post-mean
t1 <- make_table_mean("affect_post")
t2 <- make_table_mean("cog_post")
t3 <- make_table_mean("value_post")
t4 <- make_table_mean("difficulty_post")
t5 <- make_table_mean("interest_post")
t6 <- make_table_mean("effort_post")

post_mean <- rbind(t1,t2,t3,t4,t5,t6)

#post-sd
t1 <- make_table_sd("affect_post") 
t2 <- make_table_sd("cog_post")
t3 <- make_table_sd("value_post")
t4 <- make_table_sd("difficulty_post")
t5 <- make_table_sd("interest_post")
t6 <- make_table_sd("effort_post")

post_sd <- rbind(t1,t2,t3,t4,t5,t6)



#change-mean

t1 <- make_table_mean("change_affect") 
t2 <- make_table_mean("change_cog")
t3 <- make_table_mean("change_value")
t4 <- make_table_mean("change_difficulty")
t5 <- make_table_mean("change_interest")
t6 <- make_table_mean("change_effort")

change_mean <- rbind(t1,t2,t3,t4,t5,t6)

#change-sd
t1 <- make_table_sd("change_affect") 
t2 <- make_table_sd("change_cog")
t3 <- make_table_sd("change_value")
t4 <- make_table_sd("change_difficulty")
t5 <- make_table_sd("change_interest")
t6 <- make_table_sd("change_effort")

change_sd <- rbind(t1,t2,t3,t4,t5,t6)

#plain pre mean and sd
plain_pre <- cbind(pre_mean[,c(1,3)],pre_sd[,c(3)]) %>% 
  rename("Mean"="Plain") %>% rename("SD"="Plain") %>%
  mutate(Category = recode(categ, 
                           "affect_pre"="Affect", "cog_pre"="Cognitive", 
                           "value_pre"="Value", "difficulty_pre"="Difficulty",
                           "interest_pre"="Interest", "effort_pre"="Effort")) %>%
  select(Category, Mean, SD)

#plain post mean and sd
plain_post <- cbind(post_mean[,c(1,3)],post_sd[,c(3)]) %>% 
  rename("Mean"="Plain") %>% rename("SD"="Plain") %>%
  mutate(Category = recode(categ, 
                           "affect_post"="Affect", "cog_post"="Cognitive", 
                           "value_post"="Value", "difficulty_post"="Difficulty",
                           "interest_post"="Interest", "effort_post"="Effort")) %>%
  select(Category, Mean, SD)

#plain table

#plain change
plain_change <- cbind(change_mean[,c(1,3)],change_sd[,c(3)]) %>% 
  rename("Mean"="Plain") %>% rename("SD"="Plain") %>%
  mutate(Category = recode(categ, 
                           "change_affect"="Affect", "change_cog"="Cognitive", 
                           "change_value"="Value", "change_difficulty"="Difficulty",
                           "change_interest"="Interest", "change_effort"="Effort")) %>%
  select(Category, Mean, SD)


#plain table

plain_pre %>% 
  left_join(plain_post, by = "Category", suffix = c("_pre","_post")) %>%
  left_join(plain_change, by = "Category") %>%
    rename(Mean_pre_pla = Mean_pre, SD_pre_pla=SD_pre, 
         Mean_post_pla=Mean_post, SD_post_pla=SD_post,
         Mean_change_pla=Mean, SD_change_pla=SD) %>%
  kbl() %>%
  add_header_above(c(" " = 1, "Pre"=2, "Post"=2, "Change"=2 )) %>%
  add_header_above(c(" " = 1, "Plain" = 6))
  


#interesting pre mean and sd
interesting_pre <- cbind(pre_mean[,c(1,2)],pre_sd[,c(2)]) %>% 
  rename("Mean"="Interesting") %>% rename("SD"="Interesting") %>%
  mutate(Category = recode(categ, 
                           "affect_pre"="Affect", "cog_pre"="Cognitive", 
                           "value_pre"="Value", "difficulty_pre"="Difficulty",
                           "interest_pre"="Interest", "effort_pre"="Effort")) %>%
  select(Category, Mean, SD)

#interesting post mean and sd
interesting_post <- cbind(post_mean[,c(1,2)],post_sd[,c(2)]) %>% 
  rename("Mean"="Interesting") %>% rename("SD"="Interesting") %>%
  mutate(Category = recode(categ, 
                           "affect_post"="Affect", "cog_post"="Cognitive", 
                           "value_post"="Value", "difficulty_post"="Difficulty",
                           "interest_post"="Interest", "effort_post"="Effort")) %>%
  select(Category, Mean, SD)


#interesting change
interesting_change <- cbind(change_mean[,c(1,2)],change_sd[,c(2)]) %>% 
  rename("Mean"="Interesting") %>% rename("SD"="Interesting") %>%
  mutate(Category = recode(categ, 
                           "change_affect"="Affect", "change_cog"="Cognitive", 
                           "change_value"="Value", "change_difficulty"="Difficulty",
                           "change_interest"="Interest", "change_effort"="Effort")) %>%
  select(Category, Mean, SD)

#interesting table

interesting_pre %>% 
  left_join(interesting_post, by = "Category", suffix = c("_pre","_post")) %>%
  left_join(interesting_change, by = "Category") %>% 
  rename(Mean_pre_int = Mean_pre, SD_pre_int=SD_pre, 
         Mean_post_int=Mean_post, SD_post_int=SD_post,
         Mean_change_int=Mean, SD_change_int=SD) %>%
  kbl() %>%
  add_header_above(c(" " = 1, "Pre"=2, "Post"=2, "Change"=2 )) %>%
  add_header_above(c(" " = 1, "Interesting" = 6))

#combine tables

q1 <- plain_pre %>% 
  left_join(plain_post, by = "Category", suffix = c("_pre","_post")) %>%
  left_join(plain_change, by = "Category") %>%
    rename(Mean_pre_pla = Mean_pre, SD_pre_pla=SD_pre, 
         Mean_post_pla=Mean_post, SD_post_pla=SD_post,
         Mean_change_pla=Mean, SD_change_pla=SD)
  
q2 <- interesting_pre %>% 
  left_join(interesting_post, by = "Category", suffix = c("_pre","_post")) %>%
  left_join(interesting_change, by = "Category") %>% 
  rename(Mean_pre_int = Mean_pre, SD_pre_int=SD_pre, 
         Mean_post_int=Mean_post, SD_post_int=SD_post,
         Mean_change_int=Mean, SD_change_int=SD)


q1 %>% left_join(q2, by = "Category") %>% 
  kbl(caption = "SATS-36 Summary Statistics") %>%
  kable_styling() %>%
  add_header_above(c(" " = 1, "Pre"=2, "Post"=2, "Change"=2,"Pre"=2, "Post"=2, "Change"=2 )) %>%
  add_header_above(c(" " = 1, "Plain" = 6, "Interesting"=6))

```

